** basic sectioning
.
\section{Introduction}
This is the introduction section.

\subsection{Background}
This is a subsection with background information.

\subsubsection{Details}
This is a subsubsection with details.
.
<div class="body">
<div class="latex-section">Introduction</div>
<p>This is the introduction section.</p>
<div class="latex-subsection">Background</div>
<p>This is a subsection with background information.</p>
<div class="latex-subsubsection">Details</div>
<p>This is a subsubsection with details.</p>
</div>
.


** document with title
.
\title{Test Document}
\author{Test Author}
\date{January 2024}

\maketitle

\section{First Section}
Content of the first section.
.
<div class="body">
<div class="latex-title">Test Document</div>
<div class="latex-author">Test Author</div>
<div class="latex-date">January 2024</div>
<div class="latex-section">First Section</div>
<p>Content of the first section.</p>
</div>
.


** multiple sections
.
\section{First Section}
Content of first section.

\section{Second Section}
Content of second section.

\subsection{Subsection A}
Content of subsection A.

\subsection{Subsection B}
Content of subsection B.
.
<div class="body">
<div class="latex-section">First Section</div>
<p>Content of first section.</p>
<div class="latex-section">Second Section</div>
<p>Content of second section.</p>
<div class="latex-subsection">Subsection A</div>
<p>Content of subsection A.</p>
<div class="latex-subsection">Subsection B</div>
<p>Content of subsection B.</p>
</div>
.


** section with formatting
.
\section{\textbf{Bold Section Title}}
This section has a bold title.

\subsection{Subsection with \textit{italic} word}
This subsection has italic text in the title.
.
<div class="body">
<div class="latex-section"><span class="latex-textbf">Bold Section Title</span></div>
<p>This section has a bold title.</p>
<div class="latex-subsection">Subsection with <span class="latex-textit">italic</span> word</div>
<p>This subsection has italic text in the title.</p>
</div>
.
